---
title: "p8105_hw1_jg4197"
author: "Jin Ge"
date: "9/16/2019"
output: github_document
---

# Problem 1

## Problem 1.1

```{r Create a data frame, message = FALSE}
# open a library
library(tidyverse)

# make sure the reproducibility
set.seed(10)

# create a data frame
p1_df <- tibble(
  ran_samp = rnorm(8),
  vec_log = ran_samp > 0,
  vec_char = c("Problem", "1", "is","about", "writing", "a", "data", "frame"),
  vec_factor = factor(c("0", "0", "0", "1", "1", "1", "1", "2"))
)

# calculate the mean
mean(pull(p1_df, ran_samp))

```
Only `ran_samp` is a set of numbers and can be calculated for the mean. `vec_log`, `vec_char`, `vec_factor` does not work in the mean calculation.

## Problem 1.2
```{r Convert variables, eval = FALSE}

* Problem 1.2.1
# convert logistic to numeric and multiply by ran_samp
covt_log_num <- as.numeric(pull(p1_df, vec_log))
pull(p1_df, ran_samp) * covt_log_num

* Problem 1.2.2
# convert logistic to factor and multiply by ran_samp
covt_log_fact <- as.factor(pull(p1_df, vec_log))
pull(p1_df, ran_samp) * covt_log_fact

* Problem 1.2.3
# convert logistic to factor to numeric and multiply by ran_samp
covt_log_fact_numeric <- as.numeric(
  as.factor(pull(p1_df, vec_log))
)
pull(p1_df, ran_samp) * covt_log_fact_numeric


```
Only **Problem 1.2.1** and **Problem 1.2.3** can multiply with `ran_samp` since they have been converted to numeric vectors. **Problem 1.2.2** is converted to be a factor vector which cannot multiply with a numeric vector and thus the result is 8 NA meaning no content.



# Problem 2
```{r Create and save a plot}
# make sure the reproducibility
set.seed(500)

# create a data frame
p2_df <- tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_log = x + y > 1,
  vec_num = as.numeric(vec_log),
  vec_fact = as.factor(vec_log)
)

# make a scatterplot with color by logistic vector
ggplot(p2_df, aes(x = x, y = y, color = vec_log)) + geom_point()
## Comment: The logistic vector is binary and thus the scale shows two different colored points to display the different groups

# save the last graph
ggsave("E:/R Github/P8105_HW1_jg4197-for-jeff/scatterplot_Graph1.bmp")


# make a scatterplot with color by numeric vector
ggplot(p2_df, aes(x = x, y = y, color = vec_num)) + geom_point()
## Comment: The numeric vector is continuous and thus the scale shows a range of same color to display the points

# make a scatterplot with color by factor vector
ggplot(p2_df, aes(x = x, y = y, color = vec_fact)) + geom_point()
## Comment: The factor vector has two levels corresponding to logistic vector and thus the scale shows points with two different colors

```
The size of `p2_df` is `r nrow(p2_df)` and `r ncol(p2_df)`.

The mean of `x` is `r mean(pull(p2_df, x))`.

The median of `x` is `r median(pull(p2_df, x))`.

The standard deviation of `x` is `r sd(pull(p2_df, x))`.

The proportion of `vec_log` is `r mean(pull(p2_df, as.numeric(vec_log)))` and `r 1 - mean(pull(p2_df, as.numeric(vec_log)))`.

